Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-21 paper.qmd
Designed the table for supplementary

Human behavior often shows a desire for more certainty and a tendency to prefer well-separated views. This emphasizes the importance of clear and distinct clusters. For example, in the UMAP layout of the **PBMC3k** dataset suggested by @chen2023, three distant, well-separated clusters are shown. However, our model reveals that these clusters are actually close to each other in \pD{}. Additionally, the model discovers non-uniform data distribution and non-linear structures within the clusters that are not visible in the UMAP layout, demonstrating the ability of our model in uncovering hidden data characteristics.

@@

Direct links to videos for viewing online are available in .

>>>>

Human behavior often shows a desire for more certainty and a tendency to prefer well-separated views. This emphasizes the importance of clear and distinct clusters. For example, in the UMAP layout of the **PBMC3k** dataset suggested by @chen2023, three distant, well-separated clusters are shown. However, our model reveals that these clusters are actually close to each other in \pD{}. Additionally, the model discovers non-uniform data distribution and non-linear structures within the clusters that are not visible in the UMAP layout, demonstrating the ability of our model in uncovering hidden data characteristics. (added about scDEED in Appendix as well)

@@

Direct links to videos for viewing online are available in @tbl-links.

```{r}
#| label: tbl-links
#| tbl-cap: "Example videos."

links_df <- tibble(
  data = c("PBMC3k"),
  URL = c("link1")
)

links_df |>
  kableExtra::kable(format = "latex", 
                    booktabs = TRUE, 
                    label = "tbllinks") |>
  kableExtra::kable_styling(latex_options = "scale_down")
